regression analysis

### 2024-03-25 src/analysis/regression_analysis.Rmd
Finalized the makefile and updated some .r or .rmd

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fixest)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
library(rmarkdown)
```

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(fixest)
library(skimr)
library(infer)
library(modelsummary)
library(broom)
library(purrr)
library(viridis)
library(estimatr)
library(pdftools)
library(rmarkdown)
library(tinytex)
library(latexpdf)
library(latexdiffr) 
```
